\documentclass[10pt,a4paper]{article}

\usepackage[margin=0.52in,top=0.48in,bottom=0.48in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{microtype}

\definecolor{accent}{HTML}{1E4D5F}
\definecolor{textgray}{HTML}{202124}

\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.65pt}
\setlength{\emergencystretch}{3em}
\setlength{\tabcolsep}{0pt}
\linespread{0.94}
\pagenumbering{gobble}
\urlstyle{same}
\hypersetup{
  pdftitle={Umbelina Selva CV},
  pdfauthor={Umbelina Selva}
}

\titleformat{\section}
  {\bfseries\color{accent}\small}
  {}
  {0pt}
  {\MakeUppercase}
  [\vspace{-3.5pt}\titlerule]
\titlespacing*{\section}{0pt}{5pt}{2.5pt}

\newcommand{\cvitem}[2]{%
  \hangindent=0.9em\hangafter=1
  \textbf{#1} #2\par
}
\newcommand{\cventry}[4]{%
  \textbf{#1}\hfill \textcolor{textgray}{#2}\\[-0.5pt]
  \textit{#3}\hfill \textit{#4}\par
}

\begin{document}
\color{textgray}
\fontsize{8.55}{9.25}\selectfont

\begin{center}
  {\Large\bfseries\color{accent} UMBELINA SELVA}\\[2.5pt]
  Address: 108 Holywell Drive, Loughborough, Leicestershire, LE11 3JZ\\
  Mobile: (+33) 7 82 98 90 18 \quad|\quad email: \href{mailto:U.P.Selva-22@student.lboro.ac.uk}{U.P.Selva-22@student.lboro.ac.uk} \quad|\quad Nationality: french
\end{center}

\section{Profile}
A 2nd year dynamic and flexible engineering student, with a passion for teamwork and building relationships, seeking an exciting role in engineering project to develop experience and utilise knowledge and skills gained through degree.

\section{Education}
\cventry{Loughborough University, Loughborough}{2022--2027}{MEng RMCE (2nd year) Robotics, Mechatronics, and Control Engineering}{}
Grade: (1st year) 69.1\%. modules: Software engineering, Programming, Electronics, Digital systems (logic), control design, Mathematics and Dynamics.

\cventry{Blanche de Castille, Versailles}{2015--2022}{A levels and Baccalaureate}{}
Grades: A levels Mathematics (A*), Physics (A*) and Philosophy (A*). Baccalaureate with honours ``Mention très bien''.

\cventry{Blanche de Castille, Versailles}{2015--2019}{GCSEs and Brevet}{}
Grades: GCSEs (grades A*) including Mathematics, Science, French, English, Spanish, History and Geography. Brevet with honours ``Mention très bien''.

\section{Languages}
\cvitem{English:}{8 IELTS (2021)}
\cvitem{French:}{native fluent}
\cvitem{Spanish:}{level B2 (2016--2021)}

\section{Paid Employment}
\cventry{Hockey club, Versailles}{09/2019--06/2020}{Hockey Coach}{}
Managed one team of beginners under 12 for which I developed a spreadsheet, planned weekly sessions, and strived to ensure progress among my beginners. Coaching them taught me planning, responsibility and built my confidence.

\cventry{Golf restaurant, Versailles}{07/2023}{Waitress Summer Job}{}
Worked effectively with other members of the team and handled working under pressure from customers and supervisors while multi-tasking in a fast-paced environment. It taught me patience and communication.

\section{Voluntary Employment}
\cventry{French society}{09/2022--06/2024}{Media Executive}{}
Worked with the French society committee on projects to grow the society by providing information to members of the society and using my excellent digital skills to advertise our projects on social media. Operating within a team improved my collaboration skills and my time management.

\cventry{Hockey, Versailles and Loughborough}{2018--2023}{Umpire}{}
Won a prize for Umpiring an under-fifteen's tournament over the weekend, since then umpired other matches and IMS matches back in Loughborough. Got my official umpiring certification.

\section{Skills}
\cvitem{Independent Working:}{My degree frequently requires me to work independently. This year I had a couple of coursework in programming and digital systems modules. I worked on myself whilst ensuring I met the deadlines to a high standard.}
\cvitem{Teamwork:}{Working on a group project taught me to work effectively within a team, listening to each other to benefit from everyone's knowledge. As the media executive for the French society, I worked within a committee of five members, facilitating advertising and communication.}
\cvitem{Organisation:}{Throughout the year I managed attending both my outdoors activities (tennis, hockey, gym) and my lectures. To do so I implemented little study sessions regularly into my schedule in order to optimize my free time and spend more time with my friends.}
\cvitem{Communication:}{`Communication is key!' is a reminder I give everyone before every hockey match. Still to this day, I push myself to talk as much as possible on the pitch and encourage others to do so; It increases significantly the team cohesion.}
\cvitem{Adaptability:}{I have demonstrated my ability to integrate in different cultures by playing a full role in the student life at Loughborough University. I am a member of many societies and played tennis, volleyball and dodgeball for my accommodation.}

\section{Interests and Passion}
\cvitem{Field hockey:}{since 2011 (currently Loughborough AU hockey club). Competitive since 2018, won club national league in 2021 in National 1 (~second level tier one).}
\cvitem{Tennis:}{since 2010 (currently Loughborough IMS tennis matches and social sport double matches). Tennis lessons every year and tennis camps every summer.}
\cvitem{Swimming:}{since 2010 (currently university membership). Competitive level in 2015.}
\cvitem{Choir piano and guitar:}{from 2011 to 2021. Choir for ten years as soprano; 4 years of piano; 1 year of guitar.}
\cvitem{Dance:}{since 2010. Classical dance from 2010 to 2016; salsa in 2023.}
\cvitem{Girl scout:}{2009 to 2018.}
\cvitem{Art:}{since 2015. drawing for 5 years; pottery in 2023.}

\section{Career Objective}
Since as far in time as I can recall I have always had an interest in creative activities. I am reliable, strong-minded, and curious to learn more every day. Therefore, I am looking for a placement that will both stimulate my intellectual and creative capabilities in a company that relates to my career aspirations.

\section{Referees}
References available upon request.

\end{document}
